---
title: "R-HW1"
author: "Margaret He"
output: html_document
---
```{r,echo = FALSE}
ErinsFitbit <- read.csv("~/CollegeHW/STA 32/HW 1/ErinsFitbit.csv")
```
## Problem I 
* (a): Names of the columns 
```{r, echo=FALSE}
names(ErinsFitbit)
```

* (b): Number of rows
```{r, echo=FALSE}
nrow(ErinsFitbit)
```

* (c): Results from using the summary function
```{r, echo=FALSE}
summary(ErinsFitbit)
```
This function shows the frequency of each category for categorical data and presents the statistical summary for numerical data.
 
* (d): Mean of the column "Steps""
```{r, echo=FALSE}
mean(ErinsFitbit$Steps)
```

## Problem II
(Data for every day of the week)

* (a): Average steps 
```{r, echo=FALSE}
avg.steps = aggregate(Steps ~ Day,data = ErinsFitbit,mean)
avg.steps
```

* (b): Average hours of sleep  
```{r, echo=FALSE}
avg.sleep = aggregate(Sleep ~ Day,data = ErinsFitbit, mean)
avg.sleep
```

* (c): Standard deviation of steps taken 
```{r, echo=FALSE}
sd.steps = aggregate(Steps ~ Day, data = ErinsFitbit, sd)
sd.steps
```

* (d): Standard deviation of hours of sleep 
```{r, echo=FALSE}
sd.sleep = aggregate(Sleep ~ Day, data = ErinsFitbit, sd)
sd.sleep
```

## Problem III
* (a): Results from using the fivenum function
```{r, echo=FALSE}
fivenum(ErinsFitbit$Miles)
```
The fivenum function returns the minimum, the first quartile, the median, the third quartile, and the maximum.

* (b): Results from using the function table
```{r, echo=FALSE}
table(ErinsFitbit$Day)
```
The table function returns a frequency table 

* (c): Median number of hours of sleep for every month
```{r, echo=FALSE}
median.sleep = aggregate(Sleep ~ Month,data = ErinsFitbit,median)

median.sleep
```

* (d): Median distance traveled for every month
```{r, echo=FALSE}
median.distance = aggregate(Miles ~ Month,data=ErinsFitbit,median)

median.distance
```

## Problem IV 
* (a): Boxplot of the total number of steps for every day of the week

It appears that Sundays involve less activity than the other days.
```{r, echo=FALSE,fig.height= 7}
par(mfrow=c(1,1))
boxplot(Steps ~ Day,data = ErinsFitbit, main = "Steps per Day")
```

* (b): Boxplot of the total hours of sleep for every day of the week

It appears that Mondays are less restful than the other days.
```{r, echo=FALSE,fig.height= 7}
par(mfrow=c(1,1))
boxplot(Sleep ~ Day,data = ErinsFitbit, main = "Sleep per Day")
```


* (c): Based on the boxplot in part (a), there DOES appear to be outliers for Steps
```{r, echo=FALSE}
Q3 = quantile(ErinsFitbit$Steps,c(0.75))
Q1 = quantile(ErinsFitbit$Steps,c(0.25))

lower.bound = Q3 - 1.5*(Q3-Q1)
upper.bound =  Q1 + 1.5*(Q3-Q1)
any(ErinsFitbit$Steps < lower.bound |ErinsFitbit$Steps > upper.bound)
```
We have verified that the outliers occur on Wednesday, Saturday, and Sunday.

* (d): Based on the boxplot in part (b), there DOES appear to be outliers for Sleep 
```{r, echo=FALSE}
Q1 = quantile(ErinsFitbit$Sleep,c(0.25))
Q3 = quantile(ErinsFitbit$Sleep,c(0.75))
lower.bound = Q1 - 1.5*(Q3-Q1)
upper.bound = Q3 + 1.5*(Q3-Q1)
any(ErinsFitbit$Sleep < lower.bound | ErinsFitbit$Sleep > upper.bound)
```
We have verified that the outliers occur on Sunday, Monday, Thursday, Friday, and Saturday. 

*******

#Code Appendix

```
## Problem I 
* (a): Names of the columns 

names(ErinsFitbit)

* (b): Number of rows

nrow(ErinsFitbit)

* (c): Results from using the summary function

summary(ErinsFitbit)

This function shows the frequency of each category for categorical data and presents the statistical summary for numerical data.
 
* (d): Mean of the column "Steps""

mean(ErinsFitbit$Steps)

## Problem II
(Data for every day of the week)

* (a): Average steps 

avg.steps = aggregate(Steps ~ Day,data = ErinsFitbit,mean)
avg.steps

* (b): Average hours of sleep  

avg.sleep = aggregate(Sleep ~ Day,data = ErinsFitbit, mean)
avg.sleep

* (c): Standard deviation of steps taken 

sd.steps = aggregate(Steps ~ Day, data = ErinsFitbit, sd)
sd.steps

* (d): Standard deviation of hours of sleep 

sd.sleep = aggregate(Sleep ~ Day, data = ErinsFitbit, sd)
sd.sleep

## Problem III
* (a): Results from using the fivenum function

fivenum(ErinsFitbit$Miles)

The fivenum function returns the minimum, the first quartile, the median, the third quartile, and the maximum.

* (b): Results from using the function table

table(ErinsFitbit$Day)

The table function returns a frequency table 

* (c): Median number of hours of sleep for every month

median.sleep = aggregate(Sleep ~ Month,data = ErinsFitbit,median)

median.sleep

* (d): Median distance traveled for every month

median.distance = aggregate(Miles ~ Month,data=ErinsFitbit,median)

median.distance

## Problem IV 
* (a): Boxplot of the total number of steps for every day of the week

It appears that Sundays involve less activity than the other days.

par(mfrow=c(1,1))
boxplot(Steps ~ Day,data = ErinsFitbit, main = "Steps per Day")

* (b): Boxplot of the total hours of sleep for every day of the week

It appears that Mondays are less restful than the other days.

par(mfrow=c(1,1))
boxplot(Sleep ~ Day,data = ErinsFitbit, main = "Sleep per Day")

* (c): Based on the boxplot in part (a), there DOES appear to be outliers for Steps

Q3 = quantile(ErinsFitbit$Steps,c(0.75))
Q1 = quantile(ErinsFitbit$Steps,c(0.25))

lower.bound = Q3 - 1.5*(Q3-Q1)
upper.bound =  Q1 + 1.5*(Q3-Q1)
any(ErinsFitbit$Steps < lower.bound |ErinsFitbit$Steps > upper.bound)

We have verified that the outliers occur on Wednesday, Saturday, and Sunday.

* (d): Based on the boxplot in part (b), there DOES appear to be outliers for Sleep 

Q1 = quantile(ErinsFitbit$Sleep,c(0.25))
Q3 = quantile(ErinsFitbit$Sleep,c(0.75))
lower.bound = Q1 - 1.5*(Q3-Q1)
upper.bound = Q3 + 1.5*(Q3-Q1)
any(ErinsFitbit$Sleep < lower.bound | ErinsFitbit$Sleep > upper.bound)

We have verified that the outliers occur on Sunday, Monday, Thursday, Friday, and Saturday.

```