---
title: "R-HW2"
author: "Margaret He"
output: html_document
---

```{r, echo = FALSE}
ErinsFitbit <- read.csv("~/CollegeHW/STA 32/HW 1/ErinsFitbit.csv")
```

## Problem I

* (a): Number of days where the total steps were > 10,000

```{r, echo = FALSE}
num.days = length(ErinsFitbit$Day[ErinsFitbit$Steps > 10000])
num.days
```

* (b): Average number of steps taken when total sleep was < 7 hours

```{r, echo = FALSE}
num.steps = length(ErinsFitbit$Steps[ErinsFitbit$Sleep < 7])
sum.steps = sum(ErinsFitbit$Steps[ErinsFitbit$Sleep < 7])
avg.steps = sum.steps/num.steps
avg.steps
```

* (c): Number of days where the total distance walked was > 5 miles

```{r, echo = FALSE}
num.days = length(ErinsFitbit$Day[ErinsFitbit$Miles > 5])
num.days
```

* (d): Average number of miles where sleep was > 8 hours

```{r, echo = FALSE}
num.miles = length(ErinsFitbit$Miles[ErinsFitbit$Sleep > 8])
sum.miles = sum(ErinsFitbit$Miles[ErinsFitbit$Sleep > 8])
avg.miles = sum.miles/num.miles
avg.miles
```


## Problem II

* (a): Standard Deviation for vector X = 1:100 (of Miles)

```{r, echo = FALSE}
calc.sd = function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  vector = (X - Xbar)/c(1,100)*s
  std = sd(vector)
  return(std)
}
calc.sd(1:10)
```


* (b): Lower and upper boundaries of the vector X = 1:100
```{r, echo = FALSE}

```
lower:

```{r, echo = FALSE}
# find lower boundary
find.lower = function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  lower.bound = Xbar-2*s
  return(lower.bound)
}
find.lower(1:100)
```

  upper:  
```{r, echo = FALSE}
find.upper= function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  upper.bound = Xbar+2*s
  return(upper.bound)
}
find.upper(1:100)
```

* (c): Trimmed mean (after removing observations more than 3 standard deviations from the mean)

```{r, echo = FALSE}
calc.mean = function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  trimmed.mean = mean(X, trim = 3*s)  # remove certain elements from vector 
   return(trimmed.mean)
}
calc.mean(c(1:100,200,300))
```


## Problem III

* (a): Probability of flipping a head (based on 20 flips)

```{r, echo = FALSE}
sim.heads = sample(c(1,0),20, replace = TRUE)
head.prob = sum(sim.heads == 1)/length(sim.heads)
head.prob
```

* (b): Probabilities for n = 10,100,1000, 10000, 100000

```{r, echo = FALSE}
```

Probability of flipping a head for n = 10 simulations:
```{r, echo = FALSE}
sim10 = sapply(1:10, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob10 = sum(sim10)/10
prob10
```

Probability of flipping a head for n = 100 simulations:
```{r, echo = FALSE}
sim100 = sapply(1:100, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob100 = sum(sim100)/100
prob100
```

Probability of flipping a head for n = 1000 simulations:
```{r, echo = FALSE}
sim1000 = sapply(1:1000, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob1000 = sum(sim1000)/1000
prob1000
```

Probability of flipping a head for n = 10000 simulations:
```{r, echo = FALSE}
sim10000 = sapply(1:10000, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob10000 = sum(sim10000)/10000
prob10000
```

Probability of flipping a head for n = 100000 simulations:
```{r, echo = FALSE}
sim100000 = sapply(1:100000, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob100000 = sum(sim100000)/100000
prob100000
```

* (c): Calculated error of coin flip simulation done in part (c)

```{r, echo = FALSE}
```

Error for 10 simulations:
```{r, echo = FALSE}
error10 = abs(prob10-0.50)
error10
```

Error for 100 simulations:
```{r, echo = FALSE}
error100 = abs(prob100-0.50)
error100
```
Error for 1000 simulations:
```{r, echo = FALSE}
error1000 = abs(prob1000-0.50)
error1000
```

Error for 10000 simulations:
```{r, echo = FALSE}
error10000 = abs(prob10000-0.50)
error10000
```

Error for 100000 simulations:
```{r, echo = FALSE}
error100000 = abs(prob100000-0.50)
error100000
```

* (d): 
As n increases, the error appears to decrease because the difference between the statistic and the parameter decreases. The result of performing the same experiment on a large number of times yields results that are closer to the expected value, thus lowering the error.


## Problem IV

```{r, echo = FALSE}
values = as.character(1:7)
```    

* (a): Draw from a vector with 7 values (without replacement)

```{r, echo = FALSE}
one.draw = sample(values,7,replace = F)
one.draw
```

* (b): Number of orderings beginning with '1' in 100000 simulations 

```{r, echo = FALSE}
sim.draws = sapply(1:100000, function(i){
  one.draw = sample(values,7,replace = F)
  num.1starts = ifelse(one.draw[1] == "1", TRUE, FALSE)
  return(num.1starts)  
})
num.orderings = sum(sim.draws == "TRUE")
num.orderings
```

* (c): Probability that a random ordering started with a 3 and ended with a 7

```{r, echo = FALSE}
sim.draws = sapply(1:100000, function(i){
  one.draw = sample(values,7,replace = F)
  num.orderings = ifelse(one.draw[1] == "3" & one.draw[7] == "7", TRUE, FALSE)
  return(num.orderings)  
})
prob.true = sum(sim.draws == "TRUE")/(length (sim.draws))
prob.true
```

* (d): Number of unique orderings of 7 values
(permutations and no repetition is allowed)

```{r, echo = FALSE}
sim.draws = sapply(1:100000, function(i){
  one.draw = sample(values,7,replace = F)
  one.order = paste(one.draw,collapse = "")
  return(one.order)
})
uni.orderings = length(unique(sim.draws))
uni.orderings
```

*******

#Code Appendix

```
ErinsFitbit <- read.csv("~/CollegeHW/STA 32/HW 1/ErinsFitbit.csv")


## Problem I

* (a): Number of days where the total steps were > 10,000

num.days = length(ErinsFitbit$Day[ErinsFitbit$Steps > 10000])
num.days

* (b): Average number of steps taken when total sleep was < 7 hours

num.steps = length(ErinsFitbit$Steps[ErinsFitbit$Sleep < 7])
sum.steps = sum(ErinsFitbit$Steps[ErinsFitbit$Sleep < 7])
avg.steps = sum.steps/num.steps
avg.steps

* (c): Number of days where the total distance walked was > 5 miles

num.days = length(ErinsFitbit$Day[ErinsFitbit$Miles > 5])
num.days

* (d): Average number of miles where sleep was > 8 hours

num.miles = length(ErinsFitbit$Miles[ErinsFitbit$Sleep > 8])
sum.miles = sum(ErinsFitbit$Miles[ErinsFitbit$Sleep > 8])
avg.miles = sum.miles/num.miles
avg.miles

## Problem II

* (a): Standard Deviation for vector X = 1:100 (of Miles)

calc.sd = function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  vector = (X - Xbar)/c(1,100)*s
  std = sd(vector)
  return(std)
}
calc.sd(1:10)


* (b): Lower and upper boundaries of the vector X = 1:100

lower:

# find lower boundary
find.lower = function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  lower.bound = Xbar-2*s
  return(lower.bound)
}
find.lower(1:100)

  upper:  
find.upper= function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  upper.bound = Xbar+2*s
  return(upper.bound)
}
find.upper(1:100)

* (c): Trimmed mean (after removing observations more than 3 standard deviations from the mean)

calc.mean = function(i){
  X = ErinsFitbit$Miles
  Xbar = mean(X)
  s = sd(X)
  trimmed.mean = mean(X, trim = 3*s)  # remove certain elements from vector 
   return(trimmed.mean)
}
calc.mean(c(1:100,200,300))

## Problem III

* (a): Probability of flipping a head (based on 20 flips)


sim.heads = sample(c(1,0),20, replace = TRUE)
head.prob = sum(sim.heads == 1)/length(sim.heads)
head.prob

* (b): Probabilities for n = 10,100,1000, 10000, 100000


Probability of flipping a head for n = 10 simulations:
sim10 = sapply(1:10, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob10 = sum(sim10)/10
prob10

Probability of flipping a head for n = 100 simulations:

sim100 = sapply(1:100, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob100 = sum(sim100)/100
prob100

Probability of flipping a head for n = 1000 simulations:

sim1000 = sapply(1:1000, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob1000 = sum(sim1000)/1000
prob1000

Probability of flipping a head for n = 10000 simulations:

sim10000 = sapply(1:10000, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob10000 = sum(sim10000)/10000
prob10000

Probability of flipping a head for n = 100000 simulations:

sim100000 = sapply(1:100000, function(n){
  sim.heads = sample(c(1,0),n, replace = TRUE)
  prob.head = sum(sim.heads == 1)/length(sim.heads)
  return(prob.head)
})
prob100000 = sum(sim100000)/100000
prob100000

* (c): Calculated error of coin flip simulation done in part (c)

Error for 10 simulations:

error10 = abs(prob10-0.50)
error10

Error for 100 simulations:

error100 = abs(prob100-0.50)
error100

Error for 1000 simulations:

error1000 = abs(prob1000-0.50)
error1000

Error for 10000 simulations:

error10000 = abs(prob10000-0.50)
error10000

Error for 100000 simulations:

error100000 = abs(prob100000-0.50)
error100000

* (d): 
As n increases, the error appears to decrease because the difference between the statistic and the parameter decreases. The result of performing the same experiment on a large number of times yields results that are closer to the expected value, thus lowering the error.


## Problem IV


values = as.character(1:7)

* (a): Draw from a vector with 7 values (without replacement)


one.draw = sample(values,7,replace = F)
one.draw

* (b): Number of orderings beginning with '1' in 100000 simulations 

sim.draws = sapply(1:100000, function(i){
  one.draw = sample(values,7,replace = F)
  num.1starts = ifelse(one.draw[1] == "1", TRUE, FALSE)
  return(num.1starts)  
})
num.orderings = sum(sim.draws == "TRUE")
num.orderings


* (c): Probability that a random ordering started with a 3 and ended with a 7


sim.draws = sapply(1:100000, function(i){
  one.draw = sample(values,7,replace = F)
  num.orderings = ifelse(one.draw[1] == "3" & one.draw[7] == "7", TRUE, FALSE)
  return(num.orderings)  
})
prob.true = sum(sim.draws == "TRUE")/(length (sim.draws))
prob.true


* (d): Number of unique orderings of 7 values
(permutations and no repetition is allowed)


sim.draws = sapply(1:100000, function(i){
  one.draw = sample(values,7,replace = F)
  one.order = paste(one.draw,collapse = "")
  return(one.order)
})
uni.orderings = length(unique(sim.draws))
uni.orderings

```
