---
title: "R Homework 4"
author: "Margaret He"
date: "May 6th, 2016"
output: html_document
---

##Problem I

* (a): Number of successes in 40 trials

```{r, echo=FALSE}
sim1 = sum(sample(c("Success","Failure"),40,prob = c(0.05,0.95),replace = TRUE) == "Success")

sim1
```
  
* (b): Histogram Plot

```{r, echo=FALSE}
sim1 = sum(sample(c("Success","Failure"),40,prob = c(0.05,0.95),replace = TRUE) == "Success")
repeatsim = sapply(1:1000000, function(i){
  sim1 = sum(sample(c("Success","Failure"),40,prob = c(0.05,0.95),replace = TRUE) == "Success")
  return(sim1)
})
freq = names(table(repeatsim))[which.max(table(repeatsim))]

hist(repeatsim, main = "Number of successes for 1000000 repetitions",ylab = "Frequency",xlab = "# Successes")
```

* (c): shape of histogram
No the histogram is not symmetric; it's skewed right.

* (d): most frequent value 
The most frequently appearing value in (b) appears to be 3. Using R we find that it is: `r freq`.  

##Problem II
* (a): average (top) and standard deviation (bottom)

```{r, echo=FALSE}
avg = mean(repeatsim)
sd = sd(repeatsim)
avg
sd
```
* (b): probability that all students remembered their hw

```{r, echo=FALSE}
allrem = mean(repeatsim == 0)
allrem
```

* (c): probability that at least 2 students forgot their hw

```{r, echo=FALSE}
twoforget = mean(repeatsim >= 2)
twoforget
```


* (d): median number of students who forgot their hw

```{r, echo=FALSE}
the.med = median(glasses);
the.med
```


##Problem III

* (a): Histogram of population, true mean (top), and true variance (bottom)

```{r, echo=FALSE}
lynx = as.numeric(lynx)
hist(lynx, main = "Lynx",xlab = "Population")
avg = mean(lynx)
avg
the.var = var(lynx)
the.var
```

* (b): Average with sample size n = 10

```{r, echo=FALSE}
lynx = as.numeric(lynx)
index = sample(1:length(lynx), 10, replace = FALSE)
new.sample = lynx[index]
avg = mean(new.sample)
avg
```


* (c): Mean (top) and Standard Deviation (Bottom) of vector of 1000000 means (multiple simulations of part b)

```{r, echo=FALSE}
lynx = as.numeric(lynx)
lynx.function = sapply(1:1000000, function(i){
  index = sample(1:length(lynx), 10, replace = FALSE)
  new.sample = lynx[index]
  avg1 = mean(new.sample)
  return(avg1)
  })

sig = sd(lynx)
xbar = mean(lynx.function)
xbar
sample.sd = sd(lynx.function)
sample.sd
```

* (d): Differences in mean and standard deviation in parts (a) and (c)

```{r, echo=FALSE}
mean.diff = abs(avg-xbar)
sd.diff = abs(sig-sample.sd)
```

The mean of (a) and (c) are very close to each other; they differ by only `r mean.diff`. Their standard deviations showed a difference of `r sd.diff`.   


##Problem IV

* (a): Histogram from III (c)

```{r, echo=FALSE}
hist((lynx.function), main = "Distribution of means", n=40,xlab = "Average")
```

It is less skewed than the population distribution.


* (b): sample mean (top) and standard deviation (bottom) from a sample of 50 

```{r, echo = FALSE}
mean50 = mean(sample(lynx,50,replace = FALSE))
mean50
sd50 = sd(sample(lynx,50,replace = FALSE))
sd50
```

* (c): mean (top) and standard deviation (bottom) of 1000000 simulations' means

```{r, echo = FALSE}
mean.of.means = sapply(1:1000000,function(i){
  simmean = mean(sample(lynx,50,replace = FALSE))
  return(simmean)
})
finalmean = mean(mean.of.means)
finalmean
finalsd = sd(mean.of.means)
finalsd
```
The mean in III(c) stayed about the same, while the standard devation decreased.

* (d): Histogram of the vector in (c)

```{r, echo = FALSE}
hist(mean.of.means, main = "Mean Distribution, n = 50",xlab = "Average")
```
The shape is more symmetric now.


*******
#Code Appendix
  
```
##Problem I

* (a): Number of successes in 40 trials

sim1 = sum(sample(c("Success","Failure"),40,prob = c(0.05,0.95),replace = TRUE) == "Success")

sim1

* (b): Histogram Plot

sim1 = sum(sample(c("Success","Failure"),40,prob = c(0.05,0.95),replace = TRUE) == "Success")
repeatsim = sapply(1:1000000, function(i){
  sim1 = sum(sample(c("Success","Failure"),40,prob = c(0.05,0.95),replace = TRUE) == "Success")
  return(sim1)
})
freq = names(table(repeatsim))[which.max(table(repeatsim))]

hist(repeatsim, main = "Number of successes for 1000000 repetitions",ylab = "Frequency",xlab = "# Successes")

* (c): shape of histogram
No the histogram is not symmetric; it's skewed right.

* (d): most frequent value 
The most frequently appearing value in (b) appears to be 3. Using R we find that it is: `r freq`.  

##Problem II
* (a): average (top) and standard deviation (bottom)

avg = mean(repeatsim)
sd = sd(repeatsim)
avg
sd

* (b): probability that all students remembered their hw

allrem = mean(repeatsim == 0)
allrem

* (c): probability that at least 2 students forgot their hw

twoforget = mean(repeatsim >= 2)
twoforget


* (d): median number of students who forgot their hw

med = median(repeatsim)
med


##Problem III

* (a): Histogram of population, true mean (top), and true variance (bottom)

lynx = as.numeric(lynx)
hist(lynx, main = "Lynx",xlab = "Population")
avg = mean(lynx)
avg
the.var = var(lynx)
the.var


* (b): Average with sample size n = 10

lynx = as.numeric(lynx)
index = sample(1:length(lynx), 10, replace = FALSE)
new.sample = lynx[index]
avg = mean(new.sample)
avg


* (c): Mean (top) and Standard Deviation (Bottom) of vector of 1000000 means (multiple simulations of part b)

lynx = as.numeric(lynx)
lynx.function = sapply(1:1000000, function(i){
  index = sample(1:length(lynx), 10, replace = FALSE)
  new.sample = lynx[index]
  avg1 = mean(new.sample)
  return(avg1)
  })

sig = sd(lynx)
xbar = mean(lynx.function)
xbar
sample.sd = sd(lynx.function)
sample.sd


* (d): Differences in mean and standard deviation in parts (a) and (c)

mean.diff = abs(avg-xbar)
sd.diff = abs(sig-sample.sd)

The mean of (a) and (c) are very close to each other; they differ by only `r mean.diff`. Their standard deviations showed a difference of `r sd.diff`.   


##Problem IV

* (a): Histogram from III (c)

hist((lynx.function), main = "Distribution of means", n=40,xlab = "Average")

It is less skewed than the population distribution.


* (b): sample mean (top) and standard deviation (bottom) from a sample of 50 

mean50 = mean(sample(lynx,50,replace = FALSE))
mean50
sd50 = sd(sample(lynx,50,replace = FALSE))
sd50

* (c): mean (top) and standard deviation (bottom) of 1000000 simulations' means

mean.of.means = sapply(1:1000000,function(i){
  simmean = mean(sample(lynx,50,replace = FALSE))
  return(simmean)
})
finalmean = mean(mean.of.means)
finalmean
finalsd = sd(mean.of.means)
finalsd

The mean in III(c) stayed about the same, while the standard devation decreased.

* (d): Histogram of the vector in (c)

hist(mean.of.means, main = "Mean Distribution, n = 50",xlab = "Average")

The shape is more symmetric now.

```