---
title: "R HW6"
author: "Margaret He"
date: "May 27, 2016"
output: html_document
---

##Problem I

```{r, echo = FALSE}
mu = 5
normal.pop = rnorm(1000000, mean=5, sd=10)

# check whether the true mean falls within the CI
prob.within = function(n, p){
  sample = normal.pop[sample(length(normal.pop), n, replace = FALSE)]
  sig = sd(sample)
  error = (qnorm(0.975)*(sig/sqrt(n)))
  #error <- qt(0.975, df=n-1)*sig/sqrt(n)
  LB = mu - error
  UB = mu + error
  check = (p <= UB & p >= LB) #returns true or false
  return(check)
}

```

* (a): Whether the true mean falls within the 95% confidence interval for a sample size of 15

```{r, echo = FALSE}
prob.within(15, 0.95)

```
* (b): Result of checking 10,000 times whether the true mean falls within the 95% confidence interval

```{r, echo = FALSE}
sims <- replicate(10000, prob.within(15, 0.95))
table(c(sims))

```

* (c): Coverage probability of simulations from part b)

```{r, echo = FALSE}
sims <- replicate(10000, prob.within(15, 0.95))
cover.prob = (sum(sims))/ 10000
cover.prob

```

* (d): This confidence interval did not have at least a 95% coverage probability.


##Problem II

```{r, echo = FALSE}
mu = 5
exp.pop = rexp(1000000, 1/mu)

# check whether the true mean falls within the CI
prob.within2 = function(n, p){
  sample = exp.pop[sample(length(exp.pop), n, replace = FALSE)]
  sig = sd(sample)
  error = (qnorm(0.975)*(sig/sqrt(n)))
  LB = mu - error
  UB = mu + error
  check = (p <= UB & p >= LB) #returns true or false
  return(check)
}

```

* (a): Whether the true mean falls within the 95% confidence interval for a sample size of 15

```{r, echo = FALSE}
prob.within2(15, .95)

```

* (b): Result of checking 10,000 times whether the true mean falls within the 95% confidence interval

```{r, echo = FALSE}
sims <- replicate(10000, prob.within2(15, 0.95))
table(c(sims))

```

* (c): Coverage probability of simulations from part b)

```{r, echo = FALSE}
sims <- replicate(10000, prob.within2(15, 0.95))
cover.prob = (sum(sims))/ 10000
cover.prob

```

* (d): The results show that the confidence interval does not have at least a 95% coverage probability because the true mean falls within the 95% confidence interval less than 95% of the time.


##Problem III

* (a): Whether the true mean falls within the 95% confidence interval for a sample size of 60

```{r, echo = FALSE}
prob.within2(60, 0.95)

```

* (b): Result of checking 10,000 times whether the true mean falls within the 95% confidence interval

```{r, echo = FALSE}
sims <- replicate(10000, prob.within2(60, 0.95))
table(c(sims))

```

* (c): Coverage probability of simulations from part b)

```{r, echo = FALSE}
sims <- replicate(10000, prob.within2(60, 0.95))
cover.prob = (sum(sims))/ 10000
cover.prob

```

* (d): The data shows that the confidence interval does not have at least a 95% coverage probability because the true mean falls within the 95% confidence interval less than 95% of the time.

  
*******

#Code Appendix
  
```
##Problem I

mu = 5
normal.pop = rnorm(1000000, mean=5, sd=10)

# check whether the true mean falls within the CI
prob.within = function(n, p){
  sample = normal.pop[sample(length(normal.pop), n, replace = FALSE)]
  sig = sd(sample)
  error = (qnorm(0.975)*(sig/sqrt(n)))
  #error <- qt(0.975, df=n-1)*sig/sqrt(n)
  LB = mu - error
  UB = mu + error
  check = (p <= UB & p >= LB) #returns true or false
  return(check)
}


* (a): Whether the true mean falls within the 95% confidence interval for a sample size of 15


prob.within(15, 0.95)

* (b): Result of checking 10,000 times whether the true mean falls within the 95% confidence interval


sims <- replicate(10000, prob.within(15, 0.95))
table(c(sims))


* (c): Coverage probability of simulations from part b)


sims <- replicate(10000, prob.within(15, 0.95))
cover.prob = (sum(sims))/ 10000
cover.prob


* (d): This confidence interval did not have at least a 95% coverage probability.


##Problem II

mu = 5
exp.pop = rexp(1000000, 1/mu)

# check whether the true mean falls within the CI
prob.within2 = function(n, p){
  sample = exp.pop[sample(length(exp.pop), n, replace = FALSE)]
  sig = sd(sample)
  error = (qnorm(0.975)*(sig/sqrt(n)))
  LB = mu - error
  UB = mu + error
  check = (p <= UB & p >= LB) #returns true or false
  return(check)
}


* (a): Whether the true mean falls within the 95% confidence interval for a sample size of 15

prob.within2(15, .95)


* (b): Result of checking 10,000 times whether the true mean falls within the 95% confidence interval


sims <- replicate(10000, prob.within2(15, 0.95))
table(c(sims))


* (c): Coverage probability of simulations from part b)


sims <- replicate(10000, prob.within2(15, 0.95))
cover.prob = (sum(sims))/ 10000
cover.prob


* (d): The results show that the confidence interval does not have at least a 95% coverage probability because the true mean falls within the 95% confidence interval less than 95% of the time.


##Problem III

* (a): Whether the true mean falls within the 95% confidence interval for a sample size of 60


prob.within2(60, 0.95)


* (b): Result of checking 10,000 times whether the true mean falls within the 95% confidence interval

sims <- replicate(10000, prob.within2(60, 0.95))
table(c(sims))


* (c): Coverage probability of simulations from part b)


sims <- replicate(10000, prob.within2(60, 0.95))
cover.prob = (sum(sims))/ 10000
cover.prob


* (d): The data shows that the confidence interval does not have at least a 95% coverage probability because the true mean falls within the 95% confidence interval less than 95% of the time.

```
