---
title: "R-HW5"
author: "Margaret He"
date: "May 13, 2016"
output: html_document
---


##Problem I
* (a): Days it took up to and including the first rainy day
```{r, echo = FALSE}
current.weather = sample(c("R","NR"),1,prob = c(1/10,9/10))
num.days = 1
while(current.weather != "R"){
  current.weather = sample(c("R","NR"),1,prob = c(1/10,9/10))
  num.days = num.days+1
}
num.days
```

* (b):
```{r, echo = FALSE}
all.rainy = sapply (1:20000, function(i){
  current.weather = sample(c("R","NR"),1,prob = c(1/10,9/10))
num.days = 1
while(current.weather != "R"){
  current.weather = sample(c("R","NR"),1,prob = c(1/10,9/10))
  num.days = num.days+1
}
return(num.days)
})
hist(all.rainy,main = "Days until first Rain", xlab = "Number of days")
```

* (c):
```{r, echo = FALSE}
the.med = round(median(all.rainy),digits = 4)
```

The median is `r the.med`.

* (d):
```{r, echo = FALSE}
mean = round(mean(all.rainy),digits = 4)
sd= round(sd(all.rainy),digits = 4)
```

The mean is `r mean`.
The standard deviation is `r sd`.

* (e):
```{r,echo = FALSE}
prob = round(mean(all.rainy <=10 & all.rainy >= 5),digits = 4)
```
The estimated probability is `r prob`




##Problem II
* (a):
```{r, echo = FALSE}
current.person = sample(c("G","NG"),1, prob = c(0.40,0.60))
person.count = sum(current.person == "G")
num = 1
while(person.count !=4){
  current.person = sample(c("G","NG"),1, prob = c(0.40,0.60))
  person.count = person.count + sum(current.person == "G")
  num = num + 1
}
num
```

* (b):
```{r, echo = FALSE}
glasses = sapply(1:50000,function(i){
  current.person = sample(c("G","NG"),1, prob = c(0.40,0.60))
  person.count = sum(current.person == "G")
  num = 1
  while(person.count !=4){
    current.person = sample(c("G","NG"),1, prob = c(0.40,0.60))
    person.count = person.count + sum(current.person == "G")
    num = num + 1
  }
  return(num)
})
hist(glasses,main = "People until 5 Near Sighted", xlab = "Number of People")
```

* (c):
```{r, echo = FALSE}
the.med = round(median(glasses),digits = 4)
```

The median number of poeople it took until 5 were near sigthed was: `r the.med`.

* (d):
```{r, echo = FALSE}
le.mean = round(mean(glasses),digits = 4)
le.sd = round(sd(glasses),digits = 4)
```

The mean number of people it took until 5 near sighted is: `r le.mean`.
The standard deviation of the number of people it took until 5 nearsighted is: `r le.sd`.

* (e):
```{r,echo = FALSE}
prob = round(mean(glasses > 10),digits = 4)
```

The estimated probability that it took more than 10 people before 5 were found is: `r prob`.



##Problem III

* (a):
```{r, echo = FALSE}
X = rnorm(1000, mean = 2, sd = 1)
Y = rnorm(1000, mean = -2, sd = 5)
X.mean = round(mean(X),digits = 4)
X.sd = round(sd(X),digits = 4)
Y.mean = round(mean(Y),digits = 4)
Y.sd = round(sd(Y),digits = 4)
```

Vector X with mean `r X.mean` and standard deviation `r X.sd`.
Vector Y with mean `r Y.mean` and standard deviation `r Y.sd`.

* (b):
```{r, echo = FALSE}
X = rnorm(1000, mean = 2, sd = 1)
Y = rnorm(1000, mean = -2, sd = 5)
W = X + Y
W.mean = round(mean(W),digits = 4)
W.sd = round(sd(W),digits = 4)
```

Vector W with mean `r W.mean` and standard deviation `r W.sd`.

* (c):
```{r, echo = FALSE}
prob.w = round(mean(W > 3),digits = 4)
```

The probability the mean is larger than 3: `r prob.w`.

* (d):
```{r, echo = FALSE}
X = rnorm(1000, mean = 2, sd = 1)
Y = rnorm(1000, mean = -2, sd = 5)
W = X + Y
W.mean = round(mean(W),digits = 4)
W.sd = round(sd(W),digits = 4)
prob.w = round(mean(W > 3),digits = 4)

Error.mean =W.mean-0
Error.sd=	 W.sd - 3.60555127546
Error.prob =   prob.w - 1.17669681083

```

*******

#Code Appendix
  
```
##Problem I
* (a): # of sampled cards up to and including the first Ace

numcards = 1
currentcard = sample(c("A","NA"),1,prob = c(4/52,48/52))
while(currentcard != "A"){
  currentcard = sample(c("A","NA"),1,prob = c(4/52,48/52))
  numcards = numcards+1
}
numcards

* (b): Histogram of the simulation of part a) done 50,000 times

aces = sapply(1:50000,function(i){
  currentcard = sample(c("A","NA"),1,prob = c(4/52,48/52))
  numcards = 1
  while(currentcard != "A"){
    currentcard = sample(c("A","NA"),1,prob = c(4/52,48/52))
    numcards = numcards+1
  }
  return(numcards)
})

hist(aces,main = "# of Cards until first Ace", xlab = "Number of cards")


* (c): Median of the vector from part b)

med = median(aces)

* (d): Mean (top) and Std Dev. of Vector (bottom)


mean = mean(aces)
mean
std.dev = sd(aces)
std.dev


* (e): Probability that someone draws an ace for the first time between the 10th and 16th try (inclusive)

prob.first = mean(aces <=16 & aces >= 10)
prob.first



##Problem II
* (a): Number of components selected until 4 pass the test

component = sample(c("P","F"),1, prob = c(0.90,0.10))
passed = sum(component == "P")
numpicked = 1
while(passed !=4){
  component = sample(c("P","F"),1, prob = c(0.90,0.10))
  passed = passed + sum(component == "P")
  numpicked = numpicked + 1
}
numpicked


* (b): Histogram of simultation of part a) done 50,000 times

simulation = sapply(1:50000,function(i){
  component = sample(c("P","F"),1, prob = c(0.90,0.10))
  passcount = sum(component == "P")
  numpicked = 1
  while(passcount !=4){
    component = sample(c("P","F"),1, prob = c(0.90,0.10))
    passcount = passcount + sum(component == "P")
    numpicked = numpicked + 1
  }
  return(numpicked)
})
hist(simulation,main = "Components until 4 pass", xlab = "Number of Components")



* (c): Median of the vector from part b)

med = median(simulation)
med


* (d): Mean (top) and Std. Dev of Vector(bottom)

mean = mean(simulation) 
mean
std.dev = sd(simulation)
std.dev


* (e): Probability that > 6 components were selected before 4 passed the test

prob.g6 = mean(simulation > 6)
prob.g6



##Problem III

* Create a function that takes in values a, b, x, direct

func = function(a,b,x,direct){
  if(direct == "<="){
    result = punif(x,a,b,lower.tail= TRUE)
  }else if(direct == "<"){
    result = punif(x,a,b,lower.tail= TRUE)
  }else if(direct == ">="){
    result = punif(x,a,b,lower.tail = FALSE)
  }else if(direct == ">"){
    result = punif(x,a,b,lower.tail= FALSE)
  }else{
    print("missing direct parameter")
  }
}


* (a): P(X > 25.5)

a = 0 
b = 100
x = 25.5
direct = ">"
prob = func(a,b,x,direct)
prob


* (b): P(X < 2.2)

a = 2
b = 10
x = 2.2 
direct = "<"
prob = func(a,b,x,direct)
prob

* (c):

a = 1000
b = 25000
x = 5500
direct = "<="
prob = func(a,b,x,direct)
prob


* (d):

a = -24
b = -10
x = -12
direct = ">="
prob = func(a,b,x,direct)
prob


##Problem IV
* First generate the population
the.pop = rnorm(1000000)
true.var = 1


* (a): S^2(A) (top) and S^2(B) (bottom)

sample20 = sample(the.pop,20,replace=  FALSE)
estimateA = var(sample20)
estimateB = sum((sample20-mean(sample20))^2)/length(sample20)
errorA = true.var - estimateA
errorA
errorB = true.var - estimateB
errorB


* (b): Histograms of each of the 1000 simulated errors for both S^2(A) and S^2(B)

errors = sapply(1:1000,function(i){
  sim.samp = sample(the.pop,20,replace=  FALSE)
  estimateA = var(sim.samp)
  estimateB = sum((sim.samp- mean(sim.samp))^2)/length(sim.samp)
  errorA = true.var - estimateA  
  errorB = true.var - estimateB
  return(c(errorA,errorB))
})
par(mfrow = c(1,2))
hist(errors[1,],main = "Error for s^2_A",xlab = "error")
hist(errors[2,],main = "Error for s^2_B",xlab = "error")



* (c): Mean (top) and Std. Dev (bottom) for S^2(A) 


eA.mean = mean(errors[1,])
eA.mean
eA.sd = round(sd(errors[1,]),digits = 6)
eA.sd


*     Mean (top) and Std. Dev (bottom) for S^2(B)

eB.mean = mean(errors[2,])
eB.mean
eB.sd = sd(errors[2,])
eB.sd


* (d): Better estimator:
By looking at the graphs, I believe that implementing the continuity correction for a binomial random variable is important. Without the correction, the average error was 0.0345. However, with the correction, the average error was greatly reduced to 0.00004776.

```